Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-03 paper.tex
adicionada nova figura para formacao da rede
homogeneizada notacao de tipo de centralidade no superscript

The average and the dispersion were taken using circular statistics, in which each $measurement$ (data point) is represented as a unity complex number, $z=e^{i\theta}=\cos(\theta)+i\sin(\theta)$, where $\theta=measurement\frac{2\pi}{T}$, T is the period in which the counting is repeated. For example, $\theta=12\frac{2\pi}{24}=\pi$ for a message sent at $12h$ and given $T=24h$ for days. The moments $m_n$, lengths of moments $R_n$, mean angle $\theta_\mu$, and rescaled mean angle $\theta_\mu'$ are defined as:

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.3\textwidth]{figs/criaRede__}
	\caption{The formation of interaction networks from email messages. Each vertex represents a participant. A reply message from B to a message from A is regarded as evidence that B has received information from A and yields a directed edge. Multiple messages add ``weight'' to a directed edge. Further details are given in Section~\ref{intNet}.}
	\label{formationNetwork}
\end{figure}

@@

\begin{itemize}
	\item Asymmetry: $asy_i=\frac{k_i^{in}-k_i^{out}}{k_i}$.
	\item Mean of asymmetry of edges: $\mu_i^{asy}=\frac{\sum_{j\in J_i} e_{ji}-e_{ij}}{|J_i|=k_i}$, where $e_{xy}$ is 1 if there is an edge from $x$ to $y$, and $0$ otherwise. $J_i$ is the set of neighbors of vertex $i$, and $|J_i|=k_i$ is the number of neighbors of vertex $i$.
	\item Standard deviation of asymmetry of edges: $\sigma_i^{asy}=\sqrt{\frac{\sum_{j\in J_i}[\mu_{asy} -(e_{ji}-e_{ij}) ]^2  }{k_i}  }$.
	\item Disequilibrium: $dis_i=\frac{s_i^{in}-s_i^{out}}{s_i}$.
	\item Mean of disequilibrium of edges: $\mu_i^{dis}=\frac{\sum_{j \in J_i}\frac{w_{ji}-w_{ij}}{s_i}}{k_i}$, where $w_{xy}$ is the weight of edge $x\rightarrow y$ and zero if there is no such edge.
	\item Standard deviation of disequilibrium of edges: $\sigma_i^{dis}=\sqrt{\frac{\sum_{j\in J_i}[\mu_{dis}-\frac{(w_{ji}-w_{ij})}{s_i}]^2}{k_i}}$.
\end{itemize}

>>>>

Regular measures of location and dispersion, such as usual mean and
standard deviation, hold little meaning when observations take
place in a compact Riemannian manifold.
Therefore, such measures were taken using circular statistics, in which each $measurement$ (data point) is represented as a unity complex number, $z=e^{i\theta}=\cos(\theta)+i\sin(\theta)$, where $\theta=measurement\frac{2\pi}{T}$, T is the period in which the counting is repeated. For example, $\theta=12\frac{2\pi}{24}=\pi$ for a message sent at $12h$ and given $T=24h$ for days. The moments $m_n$, lengths of moments $R_n$, mean angle $\theta_\mu$, and rescaled mean angle $\theta_\mu'$ are defined as:

@@

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.44\textwidth]{figs/criaRede2_}
	\caption{The formation of interaction networks from email messages. Each vertex represents a participant. A reply message from author B to a message from author A is regarded as evidence that B received information from A and yields a directed edge. Multiple messages add ``weight'' to a directed edge. Further details are given in Section~\ref{intNet}.}
	\label{formationNetwork}
\end{figure}

@@

\begin{itemize}
	\item Asymmetry: $asy_i=\frac{k_i^{in}-k_i^{out}}{k_i}$.
	\item Mean of asymmetry of edges: $\mu_i^{asy}=\frac{\sum_{j\in J_i} e_{ji}-e_{ij}}{|J_i|=k_i}$, where $e_{xy}$ is 1 if there is an edge from $x$ to $y$, and $0$ otherwise. $J_i$ is the set of neighbors of vertex $i$, and $|J_i|=k_i$ is the number of neighbors of vertex $i$.
	\item Standard deviation of asymmetry of edges: $\sigma_i^{asy}=\sqrt{\frac{\sum_{j\in J_i}[\mu^{asy}_i -(e_{ji}-e_{ij}) ]^2  }{k_i}  }$.
	\item Disequilibrium: $dis_i=\frac{s_i^{in}-s_i^{out}}{s_i}$.
	\item Mean of disequilibrium of edges: $\mu_i^{dis}=\frac{\sum_{j \in J_i}\frac{w_{ji}-w_{ij}}{s_i}}{k_i}$, where $w_{xy}$ is the weight of edge $x\rightarrow y$ and zero if there is no such edge.
	\item Standard deviation of disequilibrium of edges: $\sigma_i^{dis}=\sqrt{\frac{\sum_{j\in J_i}[\mu^{dis}_i-\frac{(w_{ji}-w_{ij})}{s_i}]^2}{k_i}}$.
\end{itemize}
